\vspace{\sectionSpace}
\section{Parallelizing \aremsp\ Algorithm}
\label{sec:parallel_algo}

We now describe the parallel implementation of \aremsp\ algorithm 
on a shared memory system. We make the assumption about memory
model as stated in {\em OpenMP} regarding the atomic directive. We assume that
memory read/write operations are atomic and any operations issued concurrently by different processors will be executed in some unknown sequential order if
no ordering constructs are being used. However, two dependent operations issued
by the same processor will always be applied in the same order as they are
issued.
%\input{aremsp-I}
In \paremsp,the image is
divided row-wise into chunks of equal size and given to the threads. In the first step,
each thread runs {\em Scan Phase} of \aremsp\ on it's chunk simultaneously. We
initialize the label to the start index of the thread for every thread so that no 
two pixels in the image have the same label after the first step. After the first step, 
each pixel is given a provisional label. Next, the pixels at the boundary of
each chunk need to be merged to get the final labels. In the second step, we merge the boundary pixels using parallel 
implementation of Rem's Algorithm \cite{Patwary2012_PARemSP} which we call as
\merger.\ In \merger,\ if a thread wants to perform merging, it will first
acquire the necessary lock. Once it gets the lock, it will check whether the
node is still a root node. If yes, then the thread
will set the parent pointer and release the lock. On the other
hand if some other processor has altered the parent pointer so
that the node is no longer a root, the processor will release
the lock and continue executing the algorithm from its current
position. For complete reference, one can refer \cite{Patwary2012_PARemSP}. We
implement the parallel algorithm using OpenMP directives {\em pragma omp parallel} and {\em pragma omp for}. 
The pseudo code of \merger\ is given as Algorithm \ref{alg:merger}. 
The pseudo code of \paremsp\ is given as Algorithm
\ref{alg:PARemSP}.
\input{paremsp}
 \input{merger}
  
