\vspace{\sectionSpace}
\section{Proposed Algorithm}
\label{sec:proposed_algorithm}

Throughout the paper, for an $M \times N$ image, we denote $image(a)$ to denote the pixel value of pixel $a$.
We consider binary images i.e. an image containing two types of pixels:
object pixel and background pixel. Generally, we consider value of object pixel as 1 and value of background pixel as 0. The connected
component labeling problem is to assign a label to each object pixel so that connected object pixels have the same label.
In $2D$ images, there are two ways of defining connectedness: $4$-connectedness and $8$-connectedness. In this paper, we have 
only used $8$-connectedness of a pixel.


% \vspace{3mm}
\vspace{\sectionSpace}
\subsection{\nremsp\ Algorithm}

In \nremsp,\ we have used the decision tree suggested in \lrpc\ (Figure \ref{dtree})
for scanning and \rems\ union-find algorithm \remsp\ for storing label
equivalence.
The full algorithm for \nremsp\ is given as Algorithm \ref{alg:RemSP}.

\input{remsp}

In the scan step of \nremsp, we process image lines one by one using the
forward scan mask as shown in Figure \ref{fscan1}. We have used the decision tree proposed by \cite{Wu2009_LRPC} for 
determining the provisional label of current pixel $e$ as we can reduce the number of neighbors using decision tree. Instead of
examining all four neighbors of pixel, say $e$, i.e. $a$, $b$, $c$ and $d$, we only
examine the neighbors according to a decision tree as shown in Figure
\ref{dtree}\cite{Wu2009_LRPC}.
 Let $label$ denote the $2D$ array storing the labels and let $p$ denote equivalence array 
 then according to \lrpc\ algorithm,
three functions used by this decision tree are defined as follows:

$1)$. The one-argument copy function, copy(a), contains one statement:
					$label(e) = p(label(a))$\\
$2)$. The two-argument copy function, copy(c,a), contains one statements:
				$label(e) = merge(p, label(c), label(a))$\\
$3)$. The new label function sets $count$ as $label(e)$, appends $count$ to array $p$, and increments $count$ by $1$.

\input{figures}
% \input{remsp-I}
The implementation of {\em Scan\_CCLRemSP} is given as Algorithm
\ref{alg:RemSP-I}. However, the implementation of \merge\ operation in our
proposed algorithm \remsp\ is different from that of in \lrpc.\
We have used the implementation of union-find proposed by \rems\ 
for merge operation\cite{Patwary2010_RemSP, Dijkstra1976_RemSP}.\ \rems\ integrates the {\em union}
operation with a compression technique known as Splicing $(SP)$. 

In the \merge\ algorithm, if $x$ and $y$ are the nodes to be merged then we set $root_x$ to $x$ and $root_y$ to $y$. 
When $root_x$ is to be moved to $p(root_x)$, firstly $p(root_x)$ is
stored in a temporary variable $z$ then $p(root_x)$ is set to $p(root_y)$,
making the subtree rooted at $root_x$ a sibling of $root_y$ and finally
$root_x$ is set to $z$. The algorithm for \merge\ is given as Algorithm
\ref{alg:merge}. After the first step, we carry out the analysis phase using the \flatten\ algorithm. In the \flatten\ algorithm, we give smallest equivalent label of every connected component to all the pixels
which belong to that connected component. The algorithm also
generates consecutive labels. The algorithm for \flatten\ is given as Algorithm
\ref{alg:flatten}. 
\input{merge}
\input{flatten}

% \vspace{\sectionSpace}
%\input{remsp-I}
\subsection{\aremsp\ Algorithm}

In \aremsp,\ we have used the decision tree suggested in \arun\ 
for scanning and \rems\ union-find algorithm for storing label equivalence. The
full algorithm for \aremsp\ is given as Algorithm \ref{alg:ARemSP}.

In the first scan step of \aremsp,\ we process an image two lines at a time and
two pixels at a time using the mask shown in Figure \ref{fscan2}, which is
suggested in \cite{He2012_ARun}.
\input{remsp-I}
\input{aremsp}
% \input{remsp-I}



We assign the label to both $e$ and $g$ simultaneously. If both $e$ and $g$ are
background pixels, then nothing needs to be done. If $e$ is a foreground pixel and there is no foreground pixel in the mask, we assign a 
new provisional label to $e$ and if $g$ is a foreground pixel, we will assign
the label of $e$ to $g$. If there are foreground pixels in the mask, then we assign $e$ any label assigned to 
foreground pixels. In this case, if there is only one connected component in the mask then there is 
no need for label equivalence. Otherwise, if there are more than one connected component in the mask and as 
they are connected to $e$, all the labels of the connected components are
equivalent labels hence need to be merged. For all the cases, one can refer
\cite{He2012_ARun}.
However, our implementation for the merge operation is different from \cite{He2012_ARun}.
We use the implementation of union-find proposed by {\em Rem} \cite{Patwary2010_RemSP, Dijkstra1976_RemSP} for the merge operation in
\aremsp.\ Similar to \nremsp,\ we use \flatten\ for analysis phase
and generating consecutive labels. The implementation of {\em Scan\_ARemSP} is given as Algorithm
\ref{alg:ARemSP-I}.

%\input{aremsp-I}
% \input{aremsp-I}





 
