\begin{abstract}
Connected Component Labeling(CCL) is one of the most important step in pattern recognition and image processing. Connected
component labeling assigns labels to a pixel such that adjacent pixels sharing the same features are assigned the same label.
Typically, CCL requires several passes over the data. For example, in a two-pass technique, the first pass, each pixel is given
a provisional label and label equivalence information is stored. In the second pass,an actual label is given to each pixel. 
Suzuki et al have proposed two algorithms for CCL with two-pass technique called Link by Rank and Path Compression(LRPC), and ARun.
The {\em LRPC} algorithm uses a decision tree to assign provisional labels and
an array-based union-find datastructure to store label equivalence information.
The {\em ARun} algorithm employs a special scan order over the data and three
linear arrays instead of the conventional union-find datastructure.
To the best of our knowledge, there has not been any effort yet on parallelizing two-pass CCL for shared memory architecture.

We present a scalable parallel two-pass CCL algorithm called {\em PARemSP},
which employs scan strategy of {\em ARun} algorithm and the best union-find
technique called {\em RemSP} for storing label equivalence information of pixels
in a $2$-D image. In the first pass, we divide the image among threads and each
thread runs the scan strategy of {\em ARun} algorithm along with {\em RemSP}
simultaneously. As {\em RemSP} is easily parallelizable, we use the parallel
version of {\em RemSP} for merging the pixels on the boundary. Our experiments
show the scalability of {\em PARemSP} achieving speedups up to $20.1$ using $24$
cores on shared memory architecture for an image of size $22822 \times 20384$. Additionally, the parallel algorithm does not make use of any hardware specific routines, and thus is highly portable.
\end{abstract}
